model_fit

### 2025-12-03 Intro.Rmd
split intro file

bank_full <- read_delim("bank-full.csv", delim = ";", escape_double = FALSE, trim_ws = TRUE)
head(bank_full)
```

@@

@@

## We plan to use the k-fold cross validation approach. 
For consideration: Are we able to make our training sets a sort of proper stratification of our population dataset (Imbalance in amounts of customers subscribed).

```{r}
#bank_train <- 
#bank_test <- 
```

Model set up...

## Lgoistic Regression

```{r}
library(glmnet)
library(ggplot2)

#bank_glm <- glm(y ~., data = bank_train, family = binomial)
#summary(bank_glm)
```

estimate test error

## LDA and QDA

```{r}
library(MASS)

#bank_lda <- lda(y ~., data = bank_full, subset = train)
#bank_lda

#bank_qda <- qda(y ~., data = bank_full, subset = train)
```

estimate test error

## KNN
Interpretable in a different way... Can be used to identify customers similar to those that are subscirbed.

```{r}
library(class)

#bank_knn <- knn()
```

estimate test error

Optimize K value (w.r.t cross validation test error)

## GAM

```{r}
library(gam)
#bank_gam <- gam(y ~ , data = bank_train) # basis functions

## Boosting Decision Trees
require post-hoc explanation

Potential model Mixed effects model (attribute set variables to have a random effect)

>>>>

bank_full <- read_delim("data/bank-full_1.csv", delim = ';', escape_double = FALSE, trim_ws = TRUE)
head(bank_full)
```

@@

What does this mean? ^

@@

### 2025-12-03 draft_group-6.Rmd
test
split intro file

## results
(25%)

- Model comparison and assessment (Test error, confusion matrix, AUC, BIC, etc.)
- Discussion (make inferrences, determine the favored model)

## references
(2%)

>>>>

## 3. Data and Preprocessing
3.1 Dataset Description

Source: UCI Machine Learning Repository.

Number of observations and predictors.

Summary of variable types (categorical, numeric, campaign history).

3.3 Exploratory Data Analysis

Distribution of the response variable (class imbalance).

Univariate summaries: histograms, bar plots.

Key relationships between predictors and response.

## 4. Methodology
4.1 Overview of Statistical Learning Framework

Supervised binary classification.

Tradeoff between interpretability and predictive power.

4.2 Resampling Methods (ISLR Ch. 5)
4.2.1 Train/Test Split

Rationale for honest evaluation.

4.2.2 k-Fold Cross-Validation

Applied to Logistic Regression, KNN, and GAM (if included).

Used for model tuning and error estimation.

4.2.3 Bootstrap (Optional)

Estimating coefficient variability in Logistic Regression.

4.3 Candidate Models (ISLR Ch. 4 & 6)

Logistic Regression

Linear Discriminant Analysis (LDA)

Quadratic Discriminant Analysis (QDA)

K-Nearest Neighbors (KNN) with CV-selected k

Generalized Additive Models (GAM) (optional but interpretable)

4.4 Assessment Metrics (ISLR Ch. 6)

Test misclassification rate.

Sensitivity & specificity.

Confusion matrix.

ROC curve and AUC.

BIC (when applicable).

## 5. Results
5.1 Cross-Validation Findings

Optimal tuning parameters (e.g., best k for KNN).

CV-estimated test errors for each model.

5.2 Test Set Performance

Summary table: accuracy, sensitivity, specificity, AUC.

ROC curves for model comparison.

5.3 Interpretation of Key Predictors

Coefficient signs and magnitudes (Logistic).

Group separation interpretation (LDA/QDA).

Partial dependence/smooth terms (GAM).

## 6. Discussion
- Which model offers the best predictive accuracy?
- Which model is most interpretable for a marketing manager?
- How did resampling methods influence the final choice?
- Effects of class imbalance.
- Limitations and suggested future modeling directions.

Future directions: oversampling methods, modern ML models.

### 2025-12-03 model_fit.Rmd
split intro file

## We plan to use the k-fold cross validation approach. 
For consideration: Are we able to make our training sets a sort of proper stratification of our population dataset (Imbalance in amounts of customers subscribed).

```{r}
bank_train <- 
bank_test <- 
```

## Lgoistic Regression

```{r}
library(glmnet)
library(ggplot2)

bank_glm <- glm(y ~., data = bank_train, family = binomial)
summary(bank_glm)
```

estimate test error

## LDA and QDA

```{r}
library(MASS)

bank_lda <- lda(y ~., data = bank_full, subset = train)
bank_lda

bank_qda <- qda(y ~., data = bank_full, subset = train)
```

estimate test error

## KNN
Interpretable in a different way... Can be used to identify customers similar to those that are subscirbed.

```{r}
library(class)

bank_knn <- knn()
```

estimate test error

Optimize K value (w.r.t cross validation test error)

## GAM

```{r}
library(gam)
bank_gam <- gam(y ~ , data = bank_train) # basis functions

## Boosting Decision Trees
require post-hoc explanation

Potential model Mixed effects model (attribute set variables to have a random effect)

>>>>

## 2.3 Train/Test split
- Explain purpose of an honest out-of-sample evaluation.
- k-fold CV, k=5

---

# 3. Modeling

## 3.1 Logistic Regression (Baseline Model)
- Fit logistic regression.
- k-fold CV for estimated test error.
- Assess linearity and consider interactions if appropriate.
- Optional: **regularized logistic regression** (Ridge/Lasso) using CV-selected $\lambda$.

## 3.2 Linear Discriminant Analysis (LDA)
- Fit LDA model.
- k-fold CV for estimated test error.
- Check assumptions (normality, equal covariance).
- Discuss bias-variance

## 3.3 Quadratic Discriminant Analysis (QDA)
- Fit QDA model.
- k-fold CV for estimated test error.
- Discuss overfitting risk with higher model flexibility.
- Compare performance with LDA.

## 3.4 K-Nearest Neighbors (KNN)
- Standardize numeric predictors.
- Perform CV to tune **k** .
- Report best k and corresponding CV error.
- Discuss bias-variance behavior.

## 3.5 Generalized Additive Models (GAM)
- Fit GAM with smoothing splines for continuous variables.
- Use CV to choose smoothing parameters.
- Examine partial effect plots for interpretability.

## 3.6 Boosting (Most Flexible Model)
- Fit gradient boosting classifier (e.g., `gbm` or `xgboost`).
- Use cross-validation for:
  - number of trees,
  - interaction depth,
  - learning rate.
- Discuss complexity vs interpretability tradeoff. This model will be our benchmark non-interpretable model to compare interpretable models fitted above.

---

# 4. Results — Model Assessment & Comparison

## 4.1 Test Set Performance
For each model:
- Confusion matrix  
  - Accuracy and misclassification rate  
  - Sensitivity / specificity (important for minority class)  
- ROC curves and AUC

## 4.2 Comparative Evaluation
- Table summarizing all test-set performance metrics.
- Visual comparison of ROC curves.
- Discuss interpretability vs predictive quality.
